---
title: "Project Proposal"
subtitle: "due October 11, 2021 by 11:59 PM "
author: "Grace Lee and Ji Yun Hyo, TBD3"
date: "October 11th, 2021"
output: pdf_document
fontsize: 8 pt
---
# Load Packages
```{r load-packages, message = FALSE, warning = FALSE}
library(dplyr)
library(tidyverse)
library(sf)
library(viridis)
library(ggspatial) #for scale annotation
``` 

# Load Data
```{r load-data, message = F, warning = FALSE}
data <- read.csv(file = '../data/COVID_raw_12.8.csv')
tidy_data <- select(data, c('Participant_ID', 'age',"usres", "state", "race", "sex", "localsip", "localsip2", "localsip3", "leavehomeact___1", "leavehomeact___2", "leavehomeact___3", "leavehomeact___4", "leavehomeact___5", "leavehomeact___6", "leavehomeact___7", "leavehomereason___1", "leavehomereason___2", "leavehomereason___3", "leavehomereason___4", "leavehomereason___5", "leavehomereason___6", "leavehomereason___7", "localsiphours", "covidsick", "hhcovidsick", "ffcovidsick", "Classification", "covidtest", "educ", "hhincome"))
```

# Introduction and Data, including Research Questions
In response to the COVID-19 pandemic, 42 states and territories issued mandatory stay-at-home orders
between March 1 to May 31, 2020, affecting 2,355 out of 3,233 U.S. counties (CDC, 2020). These stay-athome policies reduced both population movement and person-to-person contact, which slowed the spread of
COVID-19. In a study published by Cambridge University Press in May 2020, the total number of infections
was projected to reach 287 million in the absence of stay-at-home and social distancing policies and 188
million with the enforcement of these policies, translating to 1.24 million lives saved (Thunström et al., 2020).

Due to the importance of stay-at-home orders in slowing the spread of COVID in the United States, we want
to ask if the average number of hours spent at home differed between different populations. To do so, we
used the dataset, “Associations of Urbanicity and Sociodemographic Characteristics with Protective Health
Behaviors and Reasons for Leaving the Home during COVID-19,” found on the Harvard Dataverse. The data
was collected through a 15-minute online questionnaire of U.S. adults (N = 2,441) recruited through social
media platforms such as Twitter, Instagram, and Facebook. The dataset had 66 variables corresponding
to the questionnaire questions, and we chose to focus on the survey responses pertaining to (1) age, (2)
country of residence, (3) state of residence, (4) race, (5) sex, (6) if local stay-at-home orders existed, (7) if
the participant stayed home even if no order existed, (8) if the participant stayed home even if they didn’t
know if an order existed, (9) how the participant protected themselves when leaving home, (10) reasons
for leaving home during the order, (11) average hours per day spent at home during the pandemic, (12) if
the participant had contracted COVID, (13) if anyone in the household had contracted COVID, (14) if any
close friends had contracted COVID, (15) if the participant lived in an urban, suburban, or rural area, (16)
whether the participant had been tested for COVID, (17) educational attainment, and (18) annual income.
Each participant/observation was identified by a unique participant ID.

# Glimpse

```{r glimpse, warning = FALSE}
glimpse(tidy_data)
```

# Data Analysis Plan

In order to explore the relationships between certain demographic characteristics and hours stayed at home
during the pandemic, we will conduct multiple two-sample t-tests comparing the mean number of hours
spent at home during the pandemic between different sexes, races (e.g. Asian vs. White), levels of education,
and income levels, among others. We also plan on constructing confidence intervals regarding the number
of hours spent at home for populations with and without formal stay-at-home orders. In addition, we plan
on examining the most frequently cited methods of protection from COVID used when in public as well as
reasons for leaving home during a stay-in-place order.

At present, we hypothesize that Asian people will have significantly greater average hours spent at home
than White people as they had 0.7 times the hospitalization rate of white people (CDC, 2020). We also
hypothesize that groups with income over $150,000 will have greater average hours spent at home due to
essential workers, whose incomes are lower on average, being required to leave home for work. To achieve
these results, we would need a significant p-value of under 0.05 from our t-test. The table and graph below
give us a preliminary idea of the differences in average hours spent home among different populations such as urban vs. rural and between different races.


References: 

Centers for Disease Control and Prevention. (2020, September 3). Timing of state and territorial COVID-19 stay-at-home orders and changes in population movement - United States, March 1–May 31, 2020. Centers for Disease Control and Prevention. 

Thunström, L., Newbold, S. C., Finnoff, D., Ashworth, M., &amp; Shogren, J. F. (2020, May 21). The benefits and costs of using social distancing to flatten the curve for covid-19: Journal of Benefit-Cost Analysis. Cambridge. 

```{r summmarize-hours, warning = FALSE}
number_of_hours <- tidy_data %>%
  group_by(race) %>%
  summarise_at(vars(localsiphours), list(hours = mean),na.rm = TRUE) #to summarize count

number_of_hours_two <- tidy_data %>%
  group_by(Classification) %>%
  summarise_at(vars(localsiphours), list(hours = mean),na.rm = TRUE) %>% #to summarize count
  print()

```

```{r data-analysis, fig.width = 9, fig.height= 2.5}

tidy_data$race[tidy_data$race == 0] <- "American Indian"
tidy_data$race[tidy_data$race == 1] <- "Asian"
tidy_data$race[tidy_data$race == 2] <- "Native Hawaiian"
tidy_data$race[tidy_data$race == 3] <- "African American"
tidy_data$race[tidy_data$race == 4] <- "White"
tidy_data$race[tidy_data$race == 5] <- "Mixed"
tidy_data$race[tidy_data$race == 6] <- "Unknown"

ggplot(data=number_of_hours, aes(x=race, y=hours)) +
  geom_bar(stat="identity") +
  labs (
    y = "Average Hours Remained at Home",
    x = "Race",
    title = "Number of Hours Remained at Home by Race",
    ) 

```
