---
title: "Who Stayed at Home?"
subtitle: "An Analysis of Different Demographics and Average Number of Hours Spent at Home during COVID-19"
author: "Tee Bee Dee 3 <br> Grace Lee, Ji Yun Hyo"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
# Remove any packages from this list that you're not using
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(dplyr)
library(tidyverse)
library(sf)
library(viridis)
library(ggspatial) #for scale annotation
library(ggplot2)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r load-data, include=FALSE}
# Load your data here
data <- read.csv(file = '../data/COVID_raw_12.8.csv')
tidy_data <- select(data, c('Participant_ID', 'age',"usres", "state", "race", "sex", "localsip", "localsip2", "localsip3", "leavehomeact___1", "leavehomeact___2", "leavehomeact___3", "leavehomeact___4", "leavehomeact___5", "leavehomeact___6", "leavehomeact___7", "leavehomereason___1", "leavehomereason___2", "leavehomereason___3", "leavehomereason___4", "leavehomereason___5", "leavehomereason___6", "leavehomereason___7", "localsiphours", "covidsick", "hhcovidsick", "ffcovidsick", "Classification", "covidtest", "educ", "hhincome"))

tidy_data <- tidy_data %>%
  filter(is.na(tidy_data$race)== FALSE & is.na(tidy_data$localsiphours)== FALSE)

tidy_data$race[tidy_data$race == 0] <- "Native American"
tidy_data$race[tidy_data$race == 1] <- "Asian"
tidy_data$race[tidy_data$race == 2] <- "Hawaiian"
tidy_data$race[tidy_data$race == 3] <- "African American"
tidy_data$race[tidy_data$race == 4] <- "White"
tidy_data$race[tidy_data$race == 5] <- "Mixed"
tidy_data$race[tidy_data$race == 6] <- "Unknown"

number_of_hours <- tidy_data %>%
  group_by(race) %>%
  summarise_at(vars(localsiphours), list(hours = mean),na.rm = TRUE) #to summarize count

number_of_hours_two <- tidy_data %>%
  group_by(Classification) %>%
  summarise_at(vars(localsiphours), list(hours = mean),na.rm = TRUE) #to summarize count
  
tidy_data$Classification[is.na(tidy_data$Classification)== TRUE] <- "Urban"

reasons <-c("Work", "Care for Others", "Grocery Shopping", "Essential Shopping", "Exercise", "Walk Dog", "Other")
freq_reasons <- c(sum(tidy_data$leavehomereason___1, na.rm = TRUE), sum(tidy_data$leavehomereason___2, na.rm = TRUE), sum(tidy_data$leavehomereason___3, na.rm = TRUE), sum(tidy_data$leavehomereason___4, na.rm = TRUE), sum(tidy_data$leavehomereason___5, na.rm = TRUE), sum(tidy_data$leavehomereason___6, na.rm = TRUE), sum(tidy_data$leavehomereason___7, na.rm = TRUE))
reasons_for_leaving = data.frame(reasons, freq_reasons)

pie_chart <- tidy_data %>%
  group_by(race) %>%
  count() %>%
  ungroup() %>%
  mutate(perc = n / sum(n))
```

```{r style-slides, echo = FALSE}
style_xaringan(
  title_slide_background_image = "img/watercolour_sys02_img34_teacup-ocean.jpg"
)
```


---

## Research Question

### Is average number of hours spent at home different between different populations?

- Stay-at-Home orders issued between March 1 to May 31, 2020

- Reduced population movement and person-to-person contact

---
## Dataset
- Associations of Urbanicity and Sociodemographic Characteristics with Protective Health Behaviors and Reasons for Leaving the Home during COVID-19 (Harvard Dataverse)

- Collected through online survey of U.S. adults between April and May of 2020

- Participants approached through social media platform

- Did not include essential service workers

---

## Demographics

```{r boring-regression, echo = FALSE}
# a boring regression
ggplot(pie_chart, aes(x="", y=perc, fill=race)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  labs (
    fill = "Race",
    title = "Sample Population Composition by Race",
    ) +
  theme_void()

```

---
## Demographics Summary

```{r penguins-table, echo = FALSE}
kable(pie_chart, format = "html")
```



---

## Sample Population - Hours Spent at Home
```{r bar-graph1, echo = FALSE}
# bar graphs for race
ggplot(data=number_of_hours, aes(x=race, y=hours)) +
  geom_bar(stat="identity", fill = "#003087") +
  labs (
    y = "Average Hours Remained at Home",
    x = "Race",
    title = "Number of Hours Remained at Home by Race",
    ) 
```
---

## Sample Population - Reasons 
```{r bar-graph2, echo = FALSE,out.width="60%", fig.width=8}
ggplot(data=reasons_for_leaving, aes(x=reasons, y=freq_reasons)) +
  geom_bar(stat="identity", fill = "#003087") +
  labs (
    y = "Frequency",
    x = "Reasons",
    title = "Reasons for Leaving the House",
    ) 
```

---
## Confidence Intervals by Race and Income Level

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
tidy_data <- tidy_data %>%
  mutate(asian = ifelse(race == "Asian", 1, 0)) %>%
  mutate(white = ifelse(race == "White", 1, 0)) %>%
  mutate(unknown = ifelse(race == "Unknown", 1, 0)) %>%
  mutate(africanamerican = ifelse(race == "African American", 1, 0)) %>%
  mutate(americanindian = ifelse(race == "Native American", 1, 0)) %>%
  mutate(mixed = ifelse(race == "Mixed", 1, 0)) %>%
  mutate(hawaiian = ifelse(race == "Hawaiian", 1, 0)) %>%
  mutate(noschool = ifelse(educ == 1, 1, 0)) %>%
  mutate(g1_8 = ifelse(educ == 2, 1, 0)) %>%
  mutate(g9_11 = ifelse(educ == 3, 1, 0)) %>%
  mutate(g12 = ifelse(educ == 4, 1, 0)) %>%
  mutate(technical_college = ifelse(educ == 5, 1, 0)) %>%
  mutate(four_years_college = ifelse(educ == 6, 1, 0)) %>%
  mutate(poorest = ifelse(hhincome == 1, 1, 0)) %>%
  mutate(richest = ifelse(hhincome == 12, 1, 0))
```

```{r plot-penguins, echo = FALSE, warning = FALSE, fig.alt = "Body mass vs. flipper lenght of Palmer Penguins for species Adelie and all the others combined together. There is a relatively strong, positive relationship between the two variables. The Adelie penguins are clustered together but they don't exhibit a different trend than the rest of the penguins."}
# Code hidden with echo = FALSE
# Uses modified penguins dataset from previous chunk
# Play around with height and width until you're happy with the look

```


.pull-left[

```{r confidence_intervals, echo = FALSE,out.width="100%", fig.width=8 }
dt <- tidy_data%>%
  group_by(race)%>%
  filter(race != "Hawaiian")%>%
  summarise(
    mean = mean(localsiphours),
    lci = t.test(localsiphours, conf.level = 0.95)$conf.int[1],
    uci = t.test(localsiphours, conf.level = 0.95)$conf.int[2])

pl2 <- ggplot(data = dt)
pl2 <- pl2 + geom_point(aes(x=race, y=mean), color= "blue")
pl2 <- pl2 + geom_errorbar(aes(x=race, ymin=lci, ymax= uci), width = 0.4, color ="blue", size = 1)
pl2 <- pl2 + geom_text(aes(x=race, y=lci, label = round(lci,1)), size= 2, vjust = 1)
pl2 <- pl2 + geom_text(aes(x=race, y=uci, label = round(uci,1)), size= 2, vjust = -1)
pl2 <- pl2 + theme_classic()
pl2 <- pl2 + labs(title = "Mean Hours Spent at Home with 95% Confidence Intervals")
pl2 <- pl2 + labs(x= "Race", y = "Mean Hours Spent Home")
pl2
```
]
.pull-right[
```{r confidence_intervals_two, echo=FALSE, out.width="100%", fig.width=8}
# 95% confidence interval by income level
dt <- tidy_data%>%
  group_by(hhincome)%>%
  filter(is.na(hhincome) == FALSE)%>%
  summarise(
    mean = mean(localsiphours),
    lci = t.test(localsiphours, conf.level = 0.95)$conf.int[1],
    uci = t.test(localsiphours, conf.level = 0.95)$conf.int[2])

pl2 <- ggplot(data = dt)
pl2 <- pl2 + geom_point(aes(x=as.factor(hhincome), y=mean, fill = as.factor(hhincome)), color= "blue")
pl2 <- pl2 + geom_errorbar(aes(x=hhincome, ymin=lci, ymax= uci), width = 0.4, color ="blue", size = 1)
pl2 <- pl2 + geom_text(aes(x=hhincome, y=lci, label = round(lci,1)), size= 2, vjust = 1)
pl2 <- pl2 + geom_text(aes(x=hhincome, y=uci, label = round(uci,1)), size= 2, vjust = -1)
pl2 <- pl2 + theme_classic()
pl2 <- pl2 + labs(title = "Mean Hours Spent at Home with 95% Confidence Intervals")
pl2 <- pl2 + labs(x= "Income Level", y = "Mean Hours Spent Home", fill = "okay")
pl2 <- pl2 + scale_fill_discrete(name = "Income Levels", labels = c("1 - less than $9,999", "2 - $10,000 to $19,999", "3 - $20,000 to $29,999","4 - $30,000 to $39,999", "5 - $40,000 to $49,999", "6 - $50,000 to $59,999","7 - $60,000 to $69,999", "8 - $70,000 to $79,999", "9 - $80,000 to $89,999","10 - $90,000 to $99,999", "11 - $100,000 to $150,000", "12 - over $150,000"))
pl2
```

]

---
## Confidence Intervals by Education Level and Gender
.pull-left[
```{r by_edu, echo= FALSE, out.width="100%", fig.width=8}
# 95% confidence interval by education
tidy_data$educ[tidy_data$educ == 1] <- "No School"
tidy_data$educ[tidy_data$educ == 2] <- "G1-8"
tidy_data$educ[tidy_data$educ == 3] <- "G9-12"
tidy_data$educ[tidy_data$educ == 4] <- "GED"
tidy_data$educ[tidy_data$educ == 5] <- "Some College"
tidy_data$educ[tidy_data$educ == 6] <- "4 Years College"
tidy_data$educ[tidy_data$educ == 7] <- "Not Sure"
tidy_data$educ[is.na(tidy_data$educ)] <- "Not Sure"

dt <- tidy_data%>%
  group_by(educ)%>%
  filter(educ != "G9-12")%>%
  summarise(
    mean = mean(localsiphours),
    lci = t.test(localsiphours, conf.level = 0.95)$conf.int[1],
    uci = t.test(localsiphours, conf.level = 0.95)$conf.int[2])

pl2 <- ggplot(data = dt)
pl2 <- pl2 + geom_point(aes(x=educ, y=mean), color= "blue")
pl2 <- pl2 + geom_errorbar(aes(x=educ, ymin=lci, ymax= uci), width = 0.4, color ="blue", size = 1)
pl2 <- pl2 + geom_text(aes(x=educ, y=lci, label = round(lci,1)), size= 2, vjust = 1)
pl2 <- pl2 + geom_text(aes(x=educ, y=uci, label = round(uci,1)), size= 2, vjust = -1)
pl2 <- pl2 + theme_classic()
pl2 <- pl2 + labs(title = "Mean Hours Spent at Home with 95% Confidence Intervals")
pl2 <- pl2 + labs(x= "Education Level", y = "Mean Hours Spent Home")
pl2
```
]
.pull-right[
```{r by_gender, echo= FALSE, out.width="100%", fig.width=8}

# 95% confidence interval by gender
tidy_data$sex[tidy_data$sex == 1] <- "Male"
tidy_data$sex[tidy_data$sex == 2] <- "Female"
dt <- tidy_data%>%
  filter(is.na(sex) == FALSE) %>%
  group_by(sex)%>%
  summarise(
    mean = mean(localsiphours),
    lci = t.test(localsiphours, conf.level = 0.95)$conf.int[1],
    uci = t.test(localsiphours, conf.level = 0.95)$conf.int[2])

pl2 <- ggplot(data = dt)
pl2 <- pl2 + geom_point(aes(x=as.factor(sex), y=mean), color= "blue")
pl2 <- pl2 + geom_errorbar(aes(x=sex, ymin=lci, ymax= uci), width = 0.4, color ="blue", size = 1)
pl2 <- pl2 + geom_text(aes(x=sex, y=lci, label = round(lci,1)), size= 2, vjust = 1)
pl2 <- pl2 + geom_text(aes(x=sex, y=uci, label = round(uci,1)), size= 2, vjust = -1)
pl2 <- pl2 + theme_classic()
pl2 <- pl2 + labs(title = "Mean Hours Spent at Home with 95% Confidence Intervals")
pl2 <- pl2 + labs(x= "Gender", y = "Mean Hours Spent Home")
pl2
```
]
---

## Logistic Regressions

```{r logistic_reg, echo = FALSE, results = FALSE}
tidy_data$sex=as.factor(tidy_data$sex)
tidy_data$leavehomereason___5=as.factor(tidy_data$leavehomereason___5)
tidy_data$leavehomereason___3=as.factor(tidy_data$leavehomereason___3)
tidy_data$leavehomereason___6=as.factor(tidy_data$leavehomereason___6)
tidy_data$leavehomereason___4=as.factor(tidy_data$leavehomereason___4)
tidy_data$leavehomereason___1=as.factor(tidy_data$leavehomereason___1)

# exercise
exercise_by_gender <- tidy_data
exercise_by_gender$sex = relevel(exercise_by_gender$sex, ref = "Male")
exercise_by_gender_fit <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(leavehomereason___5 ~ sex, data = exercise_by_gender, family = "binomial")
#tidy(exercise_by_gender_fit, conf.int=TRUE, exponentiate = TRUE)

# dog walking
dogwalking_by_gender <- tidy_data %>%
  filter(is.na(leavehomereason___6) == FALSE)
dogwalking_by_gender$sex = relevel(dogwalking_by_gender$sex, ref = "Male")
dogwalking_by_gender_fit <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(leavehomereason___6 ~ sex, data = dogwalking_by_gender, family = "binomial")
#tidy(dogwalking_by_gender_fit, conf.int=TRUE, exponentiate = TRUE)

# other essential shopping
essentialshop_by_gender <- tidy_data %>%
  filter(is.na(leavehomereason___4) == FALSE)
essentialshop_by_gender$sex = relevel(essentialshop_by_gender$sex, ref = "Male")
essentialshop_by_gender_fit <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(leavehomereason___4 ~ sex, data = essentialshop_by_gender, family = "binomial")
#tidy(essentialshop_by_gender_fit, conf.int=TRUE, exponentiate = TRUE)

# working
work_by_gender <- tidy_data %>%
  filter(is.na(leavehomereason___1) == FALSE)
work_by_gender$sex = relevel(work_by_gender$sex, ref = "Male")
work_by_gender_fit <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(leavehomereason___1 ~ sex, data = work_by_gender, family = "binomial")
#tidy(work_by_gender_fit, conf.int=TRUE, exponentiate = TRUE)
```

```{r visualize_grocery_shopping_logistic_regression,echo = FALSE, warning = FALSE, echo = FALSE}
# grocery shopping
grocery_by_gender <- tidy_data %>%
  filter(is.na(leavehomereason___3) == FALSE)
grocery_by_gender$sex = relevel(grocery_by_gender$sex, ref = "Male")
grocery_by_gender_fit <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(leavehomereason___3 ~ sex, data = grocery_by_gender, family = "binomial")
#tidy(grocery_by_gender_fit, conf.int=TRUE, exponentiate = TRUE)
```


```{r visualize_logistic_reg, warning = FALSE, echo = FALSE, out.width="70%", fig.width=6}
# visualize
boxLabels = c("Exercise", "Grocery Shopping", "Dog Walking", "Other Essential Shopping", "Working")

df <- data.frame(yAxis = length(boxLabels):1, 
                 boxOdds = c(0.8159074, 0.6022504, 1.0978744,0.6030671,	0.5122374), 
                  boxCILow = c(0.6600054,	0.4347917, 0.9001398, 0.4942309, 0.4141801	), 
                 boxCIHigh = c(1.006145, 0.8220798, 1.3404133, 0.7357744, 0.6337078)
                 )

(p <- ggplot(df, aes(x = boxOdds, y = boxLabels)) + 
    geom_vline(aes(xintercept = 0), size = .25, linetype = "dashed") + 
    geom_errorbarh(aes(xmax = boxCIHigh, xmin = boxCILow), size = .5, height = 
                    .2, color = "gray50") +
    geom_point(size = 3.5, color = "orange") +
    
    geom_vline(xintercept=c(1), linetype="dotted")+
    scale_x_continuous(breaks = seq(0.1, 1.5, 0.1), labels = seq(0.1, 1.5, 0.1),
                       limits = c(0.09,1.5)) +
    theme_bw()+
    theme(panel.grid.minor = element_blank()) +
    ylab("") +
    xlab("Odds ratio") +
    annotate(geom = "text", y =1.1, x = 1.5, 
                     label = "", size = 3.5, hjust = 0) + labs(subtitle = "Reference Group: Male with 95% Confidence Intervals") +
    ggtitle("Reasons for Leaving the House")
) 
```


---


## Conclusion

- No significant differences in average number of hours spent at home between different races and income levels

- Males and those with some college education spent significantly less hours in the home

- Males left the home for the purposes of grocery shopping, other essential shopping, working, and exercising

- Disproportionate representation of demographics in our population may have skew results

- Results could have implications regarding how to improve stay-at-home policies in the future

---
